---
title: "Results"
author: "Remo Schmutz"
date: "2024-05-01"
output:
  html_document: 
    fig_caption: true
    code_folding: hide
    highlight: tango
    theme: simplex
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(wesanderson)
library(rnaturalearth)
library(sf)
library(readxl)
library(janitor)
library(paletteer)
library(maps)
library(table1)
library(ggpubr)
library(kableExtra)
library(scales)
library(showtext)
library(jtools)
library(lme4)
library(brglm2)
library(gtsummary)
library(gt)
library(scico)
library(cowplot)
library(MASS)
library(tidyverse)

source("../utils/plots.R")
                                      
df <- readRDS("../data_clean/data_clean.rds") %>%
  filter(tpt_prov == 1)

df_no_TPT <- readRDS("../data_clean/data_clean.rds") |>
  filter(tpt_prov == 0)

df1 <- readRDS("../data_clean/df1.rds")
df2 <- readRDS("../data_clean/df2.rds")
df5 <- readRDS("../data_clean/df5.rds")
df5b <- readRDS("../data_clean/df5b.rds")
df6 <- readRDS("../data_clean/df6.rds")
df7 <- readRDS("../data_clean/df7.rds")
```

-   The complete dataset includes 235 observations

    -   excluding region North America there are 201 observations left

    -   excluding incomplete responses there are 199 observations left

    -   excluding high income countries there are 178 observations left

    -   excluding sites that do not offer TPT there are 172 observations left

# Data overview

```{r}
#regions
janitor::tabyl(df$region_exact) |>adorn_totals("row") %>%
  adorn_pct_formatting(digits = 0)

df %>%
  dplyr::select(country, Prev_cat.factor, Income_group) |>
  group_by(country) %>%
  summarise(
    `Number of sites` = n(),
    `HIV Prevalence` = first(Prev_cat.factor),  # Assumes all entries are the same per country
    `Income Group` = first(Income_group)  # Assumes all entries are the same per country
  ) %>%
  ungroup() |>
  kable() |>
  kable_styling(full_width = T)
```

# Site characteristic of the excluded sites

We excluded six sites from our analysis because they do not offer TPT at the time of the survey.

```{r}
country_lookup <- tibble::tribble(
  ~country_code, ~country_name,
  "IND", "India",
  "ZAF", "South Africa",
  "UGA", "Uganda",
  "KEN", "Kenya",
  "TGO", "Togo"
) 

df_no_TPT <- df_no_TPT %>%
  left_join(country_lookup, by = c("country" = "country_code")) %>%
  dplyr::select(country_name, name, region, Prev_cat.factor, Income_group, level.factor, tbhiv_integration.factor) %>%
  rename(Country = country_name,
         Name = name, 
         Region = region,
         `HIV Prevalence` = Prev_cat.factor,
         `Income Level` = Income_group,
         `Facility level of care` = level.factor,
         `Level of Integration` = tbhiv_integration.factor) |>
  arrange(Country)

df_no_TPT %>%
  gt() %>%
  cols_label(
    Country = "Country",
    Name = "Name",
    Region = "Region",
    `HIV Prevalence` = "HIV Prevalence",
    `Income Level` = "Income Level",
    `Facility level of care` = "Facility level of care",
    `Level of Integration` = "Level of Integration"
  ) %>%
  tab_options(
    table.width = pct(100)) |>
  gt::gtsave(filename = "../results/tbl_excluded.docx")
```

# Figure 1

Identifying populations for latent TB infection (LTBI) testing and TB preventive treatment after exclusion of active TB. Mapping according to WHO guidelines (see WHO consolidated guidelines, Table 1, page xi). Household contacts are defined as household contacts of people with bacteriologically confirmed pulmonary TB, regardless of HIV status. These three groups are not exclusive, there can be overlap. PLHIV can also be household contacts.

## Some exploratory plots to get an overview of the data for PLHIV

```{r}
dt <- df %>%
  dplyr::select(record_id, region, tpt_eligible_adult___77:tpt_eligible_adult___88) %>%
  rename("None" = tpt_eligible_adult___77,
         'Antiretroviral status' = tpt_eligible_adult___1,
         'Pregnancy status' = tpt_eligible_adult___2,
         'Prior TB treatment' = tpt_eligible_adult___3,
         'Degree of immunosuppression' = tpt_eligible_adult___4,
         'Contact with TB patient' = tpt_eligible_adult___5,
         'Latent TB infection status' = tpt_eligible_adult___6,
         'Other' = tpt_eligible_adult___88) %>%
  mutate(across(everything(), as.character)) |> # Convert all columns to character
  pivot_longer(names_to = "Question", values_to = "Response", cols = -c(record_id, region))

dt |>ggplot(aes(y = Question, fill = Response)) +
  geom_bar(position = "fill")

dt |>ggplot(aes(y = Question, fill = Response)) +
  geom_bar(position = "fill") +
  facet_wrap(~region)

dt |>mutate(Response = as.numeric(Response)) |>
  filter(Response != "None") |>
  group_by(record_id) |>
  summarise(count = sum(Response)) |>
  ggplot(aes(x = count)) +
  geom_histogram(binwidth = .5) +  # Set binwidth to 1 for integer counts
  scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) +  # Adjust the number of breaks
  theme_minimal() +  # Optional: change the theme
  labs(title = "Histogram of Count",
       x = "Count",
       y = "Frequency")

dt_none <- df %>%
  dplyr::select(record_id, region, tpt_eligible_adult___77:tpt_eligible_adult___88) %>%
  rename("None" = tpt_eligible_adult___77,
         'Antiretroviral status' = tpt_eligible_adult___1,
         'Pregnancy status' = tpt_eligible_adult___2,
         'Prior TB treatment' = tpt_eligible_adult___3,
         'Degree of immunosuppression' = tpt_eligible_adult___4,
         'Contact with TB patient' = tpt_eligible_adult___5,
         'Latent TB infection status' = tpt_eligible_adult___6,
         'Other' = tpt_eligible_adult___88) %>%
  mutate(across(c(`Antiretroviral status`, `Pregnancy status`, `Prior TB treatment`,
                  `Degree of immunosuppression`, `Contact with TB patient`,
                  `Latent TB infection status`, `Other`), as.numeric)) %>%
  rowwise() %>%
  mutate(Any = if_else(any(c_across(`Antiretroviral status`:`Other`) == 1), 1, 0)) %>%
  ungroup() |>dplyr::select(record_id, None, Any) |>summarise(sum1 = sum(None), sum2 = sum(Any))
```

```{r}
fig.1 <- fig1("", pct = T)
fig.1
ggsave("../results/fig1.png", plot = fig.1, width = 18, height = 12, units = "cm", dpi = 300)
```

### Panel

```{r, fig.height=15, fig.width=11, message=F, warning=F}
fig1a <- fig1("region") + 
  labs(title = "a | By region")

ggsave("../results/fig1a.png", plot = fig1a, width = 18, height = 12, units = "cm", dpi = 300)

fig1b <- fig1("HBC_ANY") + 
  labs(title = "b | By TB burden")

ggsave("../results/fig1b.png", plot = fig1b, width = 18, height = 12, units = "cm", dpi = 300)

fig1c <- fig1("HIV Prevalence") + 
  labs(title = "c | By national HIV prevalence")

ggsave("../results/fig1c.png", plot = fig1c, width = 18, height = 12, units = "cm", dpi = 300)

fig1d <- fig1("Level of integration") + 
  labs(title = "d | By level of HIV/TB service integration")
  
ggsave("../results/fig1d.png", plot = fig1d, width = 18, height = 12, units = "cm", dpi = 300)

fig.1.panel <- ggarrange(fig1a, fig1b, fig1c, fig1d,
                 common.legend = TRUE, 
                 ncol = 2, nrow = 2,
                 legend = "bottom", 
                 widths = c(1.6,1))
                 
fig.1.panel

ggsave("../results/fig1_panel.png", plot = fig.1.panel, width = 16, height = 16, units = "cm", dpi = 300)
```

# Figure 2

Barriers to TPT administration: \*\*11.15 What are the most important barriers to initiating patients with HIV on TPT at this facility? Check all that apply\*\*  

```{r, fig.cap="Figure 2: Proportion of clinics responding to the questions regarding specific boundaries to initiating patients with HIV on TPT at the clinic. Also, if somebody in the clinic received formal training for TPT."}
fig.2 <- fig2("", pct = T)
fig.2
ggsave("../results/fig2.png", plot = fig.2, width = 18, height = 12, units = "cm", dpi = 300)
```

### Panel

```{r, fig.height=15, fig.width=11, message=F, warning=F}
fig2a <- fig2("HBC_ANY") + theme(strip.text.y.right = element_blank(), 
                                 axis.title.x.bottom = element_blank()) +
    scale_x_continuous(
      labels = function(x) paste0(format(x * 100, digits = 2), "%"),
      breaks = c(0, 1)) +
  labs(title = "a | Stratified by high TB burden countries")
  
fig2b <- fig2("region") + theme(axis.text.y = element_blank(), 
                                axis.title.x.bottom = element_blank()) +  scale_x_continuous(
      labels = function(x) paste0(format(x * 100, digits = 2), "%"),
      breaks = c(0, 1))+
    labs(title = "b | Stratified by region")

fig2c <- fig2("Income Level") + theme(strip.text.y.right = element_blank(), 
                                      axis.title.x.bottom = element_blank()) +  scale_x_continuous(
      labels = function(x) paste0(format(x * 100, digits = 2), "%"),
      breaks = c(0, 1)) +
    labs(title = "c | Stratified by Income Level")

fig2d <- fig2("HIV Prevalence") + theme(axis.text.y = element_blank(), 
                                        axis.title.x.bottom = element_blank()) +  scale_x_continuous(
      labels = function(x) paste0(format(x * 100, digits = 2), "%"),
      breaks = c(0, 1)) +
    labs(title = "d | Stratified by HIV Prevalence")

fig2e <- fig2("Level of integration") + 
  theme( strip.text.y.right = element_blank(),
        axis.title.x.bottom = element_blank()) +  
  scale_x_continuous(
    labels = function(x) paste0(format(x * 100, digits = 2), "%"),
    breaks = c(0, 1)) +
    labs(title = "e | Stratified by Level of Integration")

fig.2 <- ggarrange(fig2a, fig2b, fig2c, fig2d, fig2e, 
                 common.legend = TRUE, 
                 ncol = 2, nrow = 3,
                 legend = "bottom", 
                 widths = c(1.5, 1))

ggsave("../results/fig2.png", plot = fig.2, width = 16, units = "cm")
```

# Figure 3

-   Proportion of sites who responded "Yes" to the following question: "11.6 Does this HIV clinic (or a co-located TB clinic) currently provide TB preventive therapy (TPT)?".

-   

    (a) Location of sites, Adherence to any recommendation for (b) PLHIV, (c) other people at risk and (d) other people at risk.

```{r}
#preperation

coords <- read.csv("../data_clean/coordinates_sites.csv") %>%
  separate(coord, into = c("lat", "long"), sep = ",", convert = TRUE) |>
  filter(record_id %in% df$record_id)

world <- map_data("world") 

df3 <- df1 |>
  group_by(record_id, who_group) |>
  dplyr::summarize(any_yes = ifelse(any(category == "Yes"), 1, 0), .groups = 'drop')  |>
  left_join(df |>dplyr::select(record_id, region_exact), by = "record_id") 

## household ##

fig3a <- fig3(variable = "People living with HIV") +
  labs(title = "a | People living with HIV") +
  theme(plot.margin = unit(c(0,0,0,0.01), "cm"))

fig3b <- fig3(variable = "Household contacts")  +
  labs(title = "b | Household contacts") +
   theme(plot.margin = unit(c(0,0.01,0,0), "cm"))

fig3c <- fig3(variable = "Other people at risk") +
  labs(title = "c | Other people at risk") +
    theme(plot.margin = unit(c(0,0.01,0,0), "cm")) 

fig.3 <- ggarrange(fig3a, fig3b, fig3c,
                           common.legend = TRUE, 
                           legend = "right",   
                           ncol = 1)
ggsave("../results/fig3.png", plot = fig.3, width = 12, height = 16, units = "cm", dpi = 300)
```

# Figure 5

### Top 5

```{r}
df5_top5 <- df5 %>%
  dplyr::select(`6-month isoniazid (6H)` : `Once-weekly isoniazid-rifapentine for 12 weeks (3HP)`) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Response") %>%
  group_by(Variable, Response) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  group_by(Variable) %>%
  mutate(Proportion = Count / sum(Count)) %>%
  ungroup() %>%
  # Adding calculation for good responses
  group_by(Variable) %>%
  summarise(
    Prop_yes = sum(Proportion[Response %in% c("Adults & Children", "Adults", "Children")]),
    .groups = 'drop'
  ) %>%
  arrange(desc(Prop_yes)) |>
  slice_head(n = 5) 

ordered_vars <- rev(df5_top5$Variable)

lvl <- c("Don't know", "Not offered", "Children", "Adults", "Adults & Children")
lvl_rev <- c("Adults & Children", "Adults", "Children", "Not offered", "Don't know")

custom_colors <- c("Adults & Children" = "#8ac0ff",  
                     "Adults" = "#abe1ff",  
                     "Children" = "#d0f2ff",  
                     "Not offered" = "#fde9d8",  
                     "Don't know" = "#d3d3d3")

df5 %>%
  dplyr::select(`6-month isoniazid (6H)` : `Once-weekly isoniazid-rifapentine for 12 weeks (3HP)`) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Response") |>
  filter(Variable %in% ordered_vars) |>
  mutate(Variable = factor(Variable, levels = ordered_vars),
         Variable = fct_recode(Variable, 
                          "Once-weekly isoniazid-rifapentine\nfor 12 weeks (3HP)" = "Once-weekly isoniazid-rifapentine for 12 weeks (3HP)")) %>%
   ggplot(aes(y = Variable, 
               fill = factor(Response, levels = lvl, exclude = NULL))) +
    geom_bar(position = "fill") +
      labs(
      title = "", 
      y = "", 
      x = "Proportion of clinics (%)") +
    theme_minimal() +
    theme(
      axis.text.y = element_text(hjust = 1, size = 8),
      legend.position = "bottom",
      legend.key.size = unit(0.3, "cm"), plot.margin = unit(c(0,0.5,0,0), "cm")) +
    scale_fill_manual(
      values = custom_colors,
      breaks = lvl_rev,
      name = NULL) +
    scale_x_continuous(
      expand = c(0,0), 
      labels = function(x) paste0(format(x * 100, digits = 2)),
      breaks = c(0, 0.25, 0.5, 0.75,  1))+
    geom_vline(xintercept = 0.5, linetype = "dashed", color = "white")
```

```{r}
fig.5 <- fig5("")
fig.5
ggsave("../results/fig5.png", plot = fig.5, width = 18, height = 12, units = "cm", dpi = 300)
```

### Supplementary table

```{r}
df5 |>
  tbl_summary(by = HBC_ANY,
              include = c(`6-month isoniazid (6H)`,
                          `9-month isoniazid (9H)`,
                          `12-month isoniazid (12H)`,
                          `36/Lifetime isoniazid (36/Lifetime H)`,
                          `3-month rifampicin (3R)`,
                          `4-month rifampicin (4R)`,
                          `3-month isoniazid-rifampicin (3HR)`,
                          `Once-weekly isoniazid-rifapentine for 12 weeks (3HP)`,
                          `Once-daily isoniazid-rifapentine for 1 month (1HP)`,
                          `Regimens for MDR-TB exposure`,
                          Other)) |>
  modify_header(all_stat_cols() ~"**{level}**<br>N = {n}") 
```

### Analysis: Associations with RIF-based regimen

Every site is included. The outcome 'RIF' is defined as 1, if this site offers any RIF-based treatment and as 0 if not.

```{r}
df5_model <- df5 %>%
  mutate(
         RIF = as.integer(if_any(c("3-month rifampicin (3R)",
                                                        "4-month rifampicin (4R)",
                                                        "3-month isoniazid-rifampicin (3HR)",
                                                        "4-month isoniazid-rifampicin (4HR)",
                                                        "Once-weekly isoniazid-rifapentine for 12 weeks (3HP)",
                                                        "Once-daily isoniazid-rifapentine for 1 month (1HP)"), ~ .x %in% c("Adults", "Children", "Adults & Children"))),
         INH = as.integer(if_any(c("6-month isoniazid (6H)",
                                                        "9-month isoniazid (9H)",
                                                        "12-month isoniazid (12H)",
                                                        "36/Lifetime isoniazid (36/Lifetime H)"), ~ .x %in% c("Adults", "Children", "Adults & Children"))))

df5_model$`Income Level` <- droplevels(df5_model$`Income Level`)
df5_model$HBC_ANY <- relevel(df5_model$HBC_ANY, ref = "No")
df5_model$region <- relevel(df5_model$region, ref = "Asia-Pacific")
df5_model$`Level of integration` <- relevel(df5_model$`Level of integration`, ref = "Full")
df5_model$`HIV Prevalence` <- relevel(df5_model$`HIV Prevalence`, ref = "High")
df5_model$`Income Level` <- relevel(df5_model$`Income Level`, ref = "Upper middle")

df5_model |>
  tbl_summary(include = c(
                          region, HBC_ANY, `Level of integration`, `Income Level`, `HIV Prevalence`, `LTBI testing`, `TPT training`, `Facility level of care`), 
              digits = list(everything() ~ c(0))) 
```

#### Univariable

```{r, warning=FALSE, message=FALSE}
df5_model %>%
    tbl_uvregression(include = c(`Level of integration`, 
                                 `Income Level`, 
                                 `HIV Prevalence`, 
                                 HBC_ANY,  
                                 `TPT training`, 
                                 `Facility level of care`,
                                 `LTBI testing`, 
                                 region), 
      method = glm,
      y = RIF,
      method.args = list(family = binomial(link = "logit"), method = "brglmFit"),
      pvalue_fun = ~ifelse(. < 0.01, "<0.01", style_sigfig(., digits = 2)),
      exponentiate = TRUE,
      hide_n = TRUE, add_estimate_to_reference_rows = TRUE, label = list(region ~ "Region",
                                                                         HBC_ANY ~ "High burden country")) |>
    modify_table_body(
      ~mutate(.x, ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
  add_global_p() |> 
  as_gt() |> 
  gt::gtsave(filename = "../results/tbl_rif.docx")
```

### Panel

```{r, fig.height=15, fig.width=11, message=F, warning=F}
fig5a <- fig5("region") + 
  theme(strip.text.y.right = element_blank(), 
        axis.title.x.bottom = element_blank()) +
  scale_x_continuous(
    labels = function(x) paste0(format(x * 100, digits = 2), "%"),
    breaks = c(0, 1)) +
labs(title = "a | By region")

fig5b <- fig5("HBC_ANY") + 
  theme(axis.text.y = element_blank(), 
        axis.title.x.bottom = element_blank()) +  
  scale_x_continuous(
    labels = function(x) paste0(format(x * 100, digits = 2), "%"),
    breaks = c(0, 1))+
  labs(title = "b | By TB burden")

fig5c <- fig5("HIV Prevalence") + 
  theme(strip.text.y.right = element_blank(), 
        axis.title.x.bottom = element_blank()) +  
  scale_x_continuous(
      labels = function(x) paste0(format(x * 100, digits = 2), "%"),
      breaks = c(0, 1))+
  labs(title = "c | By national HIV prevalence")

fig5d <- fig5("Level of integration") + 
  theme(axis.text.y = element_blank(), 
        axis.title.x.bottom = element_blank()) +  scale_x_continuous(
          labels = function(x) paste0(format(x * 100, digits = 2), "%"),
          breaks = c(0, 1))+
  labs(title = "d | By level of HIV/TB service integration")

fig5e <- fig5("Level of integration") + 
  theme(strip.text.y.right = element_blank(), 
        axis.title.x.bottom = element_blank()) +  
  scale_x_continuous(
    labels = function(x) paste0(format(x * 100, digits = 2), "%"),
    breaks = c(0, 1))+
  labs(title = "e | Stratified by Level of Integration")

fig5f <- fig5("LTBI testing") + 
  theme(axis.text.y = element_blank(), 
        axis.title.x.bottom = element_blank()) +  
  scale_x_continuous(
    labels = function(x) paste0(format(x * 100, digits = 2), "%"),
    breaks = c(0, 1))+
  labs(title = "f | Stratified by LTBI testing")

fig.5.panel <- ggarrange(fig5a, fig5b, fig5c, fig5d,
                 common.legend = TRUE, 
                 ncol = 2, nrow = 2,
                 legend = "bottom", 
                 widths = c(1.8, 1))
fig.5.panel

ggsave("../results/fig5_panel.png", plot = fig.5.panel, width = 16, height = 16, units = "cm", dpi = 300)
```

# Table 1

```{r}
theme_gtsummary_journal(journal="jama")

tbl1_overall <- df6 |>
  tbl_summary(
              include = c(
                          `Population the center serves`, 
                          `Facility location`, 
                          `Facility level of care`, 
                          `Level of integrated TB/HIV services`),
              digits = list(everything() ~ c(0))) |> 
  modify_header(all_stat_cols(FALSE) ~ "N = {n}") 

tbl1B <- df6 |>
  tbl_summary(by = region,
              include = c(
                          `Population the center serves`, 
                          `Facility location`, 
                          `Facility level of care`, 
                          `Level of integrated TB/HIV services`), 
              digits = list(everything() ~ c(0))) |>
   modify_header(all_stat_cols(FALSE) ~ "**{level}**<br>N = {n}")

tbl_merge(
  tbls = list(tbl1_overall, tbl1B),
  tab_spanner = c("Overall", "Region")) |>
  as_gt() |> 
  gt::gtsave(filename = "../results/tbl1.docx")
```

# Table 2

```{r}
theme_gtsummary_journal(journal="jama")

### Base table without screening ###

tbl2_overall <- df7 |>
  tbl_summary(
              include = c(`TB symptom screening`, 
                          `Anyone attended a formal training on TPT provision`,
                          `TB infection testing to check eligibility of PLHIV to receive TPT`),
              digits = list(everything() ~ c(0))) |>
  modify_header(stat_0 ~ "N = {n}")

tbl2B <- df7 |>
  tbl_summary(by = region,
              include = c(`TB symptom screening`, 
                          `Anyone attended a formal training on TPT provision`,
                          `TB infection testing to check eligibility of PLHIV to receive TPT`),
              digits = list(everything() ~ c(0))) |>
  modify_header(all_stat_cols(FALSE) ~ "**{level}**<br>N = {n}")

tbl2a <- tbl_merge(
  tbls = list(tbl2_overall, tbl2B),
  tab_spanner = c("Overall", "Region"))|>
  as_gt() |>
  gt::gtsave(filename = "../results/tbl2.docx")
```

# Table 3

-   We compare the odds ratios for adherence to any of the WHO recommendations between different covariates. Use Figure 1 as a reference for the analysis.

    -   Outcome 1: Adherence to any of the recommendations for PLHIV (4 subgroups).

    -   Outcome 2: Adherence to any of the recommendations for Household contacts (4 subgroups).

    -   Outcome 3: Adherence to any of the recommendations for other people at risk (11 subgroups).

-   Therefore, the outcome variable is 'any_yes' (=0 if non of the WHO recommendations where adhered to, =1 if any of the WHO recommendations where adhered to).

-   The standard procedure for calculating the odds ratio fail for this dataset because **`Facility level of care:`District hospital** pefectly predicts the outcome (the whole column would be 0 for Fishers Exact test). The $\chi^2$-Test is also not applicable because of the low cell counts.

-   I use univariate firth logistic regression models, which applies a penalized likelihood approach, which adjusts the likelihood function to prevent the infinite likelihood estimates that result from complete seperation.

```{r}
df7 <- df1 |>
  group_by(record_id, who_group) |>
  dplyr::summarize(any_yes = ifelse(any(category == "Yes"), 1, 0), .groups = 'drop',
                   sum_yes = sum(category == "Yes"))   |>
  left_join(df |>dplyr::select(record_id, tbhiv_integration.factor, Income_group, Prev_cat.factor, HBC_ANY, tpt_training.factor, level.factor, region, ltbi_ligibility.factor), by = "record_id") |>
  rename(
    'Level of integration' = tbhiv_integration.factor,
    'Income Level' = Income_group, 
    'HIV Prevalence' = Prev_cat.factor,
    'High burden country' = HBC_ANY,
    'TPT training' = tpt_training.factor,
    'Facility level of care' = level.factor,
    'Region' = region,
    'LTBI testing to determine eligibility of PLHIV to receive TPT' = ltbi_ligibility.factor) |>
  mutate(`Income Level` = as.factor(`Income Level`),
         `TPT training` = as.factor(case_when(`TPT training` %in% c(NA, "Dont Know") ~ NA,
                                    TRUE ~ `TPT training`)))

df7$`Level of integration` <- relevel(df7$`Level of integration`, ref = "No")
df7$`Income Level` <- relevel(df7$`Income Level`, ref = "Low")
df7$`HIV Prevalence` <- relevel(df7$`HIV Prevalence`, ref = "Low")
df7$`TPT training` <- relevel(df7$`TPT training`, ref = "No")
df7$`TPT training` <- droplevels(df7$`TPT training`)
df7$`Facility level of care` <- relevel(df7$`Facility level of care`, ref = "Regional, provincial or university hospital")
levels(df7$`Facility level of care`) <- c("Health centre", "District hospital", "Regional or provincial hospital", "Missing")
df7$`Facility level of care` <- droplevels(df7$`Facility level of care`)
df7$Region <- relevel(df7$Region, ref = "Asia-Pacific")
df7$`LTBI testing to determine eligibility of PLHIV to receive TPT` <- relevel(df7$`LTBI testing to determine eligibility of PLHIV to receive TPT`, ref = "No")
df7$`High burden country` <- factor(df7$`High burden country`, 
                            levels = c("HBC", "Not HBC"),  # current levels
                            labels = c("Yes", "No"))       # new labels
df7$`High burden country` <- relevel(df7$`High burden country`, ref = "No")
df7$`Income Level` <- droplevels(df7$`Income Level`)

plhiv <- df7 |>filter(who_group == "People living with HIV") |>
  dplyr::select(-record_id, -who_group) |>
  mutate(sum_yes = factor(sum_yes,ordered = T))

household <- df7 |>filter(who_group == "Household contacts") |>
  dplyr::select(-record_id, -who_group) |>
  mutate(sum_yes = factor(sum_yes,ordered = T))

oPaR <- df7 |>filter(who_group == "Other people at risk") |>
  dplyr::select(-record_id, -who_group) |>
  mutate(sum_yes = factor(sum_yes,ordered = T),
         sum_yes = factor(case_when(sum_yes %in% c("8","9","10","11") ~ "High",
                                    sum_yes %in% c("4","5","6", "7") ~ "Medium",
                                    sum_yes %in% c("1","2","3") ~ "Low",
                                    sum_yes %in% c("0") ~ "No"), ordered = T))

oPaR$sum_yes <- factor(oPaR$sum_yes, levels = c("No", "Low", "Medium", "High"))
```

### Binomial

In the end this is probably the model that makes the most sense. For each record_id we have the number of recommendations adhered to (sum_yes) and the number of recommendations not adhered to (sum_no). We can model this as a binomial distribution with the number of trials being the sum of the two and the number of successes being the sum_yes.

```{r}
df7_binomial <- df1 |>
  mutate(Yes = ifelse(category == "Yes", 1, 0),
         No = ifelse(category == "No", 1, 0)) %>%
  group_by(record_id, who_group) |>
  dplyr::summarize(yes = sum(Yes),
                   no = sum(No), .groups = "drop") |>
  left_join(df |> 
              dplyr::select(record_id, tbhiv_integration.factor, Income_group, Prev_cat.factor, HBC_ANY,
                            tpt_training.factor, level.factor, region), by = "record_id") |>
  rename(
    'Level of integration' = tbhiv_integration.factor,
    'Income Level' = Income_group, 
    'HIV Prevalence' = Prev_cat.factor,
    'High burden country' = HBC_ANY,
    'TPT training' = tpt_training.factor,
    'Facility level of care' = level.factor,
    'Region' = region) |>
  mutate(`Income Level` = as.factor(`Income Level`),
         `TPT training` = as.factor(case_when(`TPT training` %in% c(NA, "Dont Know") ~ NA,
                                    TRUE ~ `TPT training`))) |> 
  ungroup()

df7_binomial$`Level of integration` <- relevel(df7_binomial$`Level of integration`, ref = "No")
df7_binomial$`Income Level` <- relevel(df7_binomial$`Income Level`, ref = "Upper middle")
df7_binomial$`HIV Prevalence` <- relevel(df7_binomial$`HIV Prevalence`, ref = "Low")
df7_binomial$`TPT training` <- relevel(df7_binomial$`TPT training`, ref = "No")
df7_binomial$`TPT training` <- droplevels(df7_binomial$`TPT training`)
df7_binomial$`Facility level of care` <- relevel(df7_binomial$`Facility level of care`, ref = "District hospital")
df7_binomial$`Facility level of care` <- droplevels(df7_binomial$`Facility level of care`)
df7_binomial$Region <- relevel(df7_binomial$Region, ref = "Africa")
df7_binomial$`High burden country` <- relevel(df7_binomial$`High burden country`, ref = "No")
df7_binomial$`Income Level` <- droplevels(df7_binomial$`Income Level`)

plhiv_binomial <- df7_binomial |> 
  filter(who_group == "People living with HIV") |>
  dplyr::select(-record_id, -who_group)

household_binomial <- df7_binomial |>
  filter(who_group == "Household contacts") |>
  dplyr::select(-record_id,-who_group)

oPaR_binomial <- df7_binomial |>
  filter(who_group == "Other people at risk") |>
  dplyr::select(-record_id, -who_group) 

fit_model_uni_binomial <- function(data) {
  data %>%
    tbl_uvregression(
      y = cbind(yes, no),
    formula = "{y} ~ {x}",
    exponentiate = TRUE,
    method = glm,
    method.args = list(family = binomial(link= "logit")),
       pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 2)),
       hide_n = TRUE, 
       add_estimate_to_reference_rows = TRUE) |>
     modify_table_body(
       ~mutate(.x, ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()
}

# Combine datasets into a list
dataset_list_binomial <- list(plhiv_binomial,household_binomial,oPaR_binomial)

# Apply the univariate model function to each dataset
tbls_binom <- lapply(dataset_list_binomial, fit_model_uni_binomial)

# Merge the tables with tab spanners
tbl_merge(
  tbls = tbls_binom,
  tab_spanner = c("People living with HIV", "Household contacts", "Other people at risk")) |> 
  as_gt() |> 
  gt::gtsave(filename = "../results/tbl3_binomial.docx")
```

#### Multivariable

```{r}
fit1 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `HIV Prevalence` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = plhiv_binomial, family = binomial(link = "logit"), method = "brglmFit")

fit2 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `HIV Prevalence` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = household_binomial, family = binomial(link = "logit"), method = "brglmFit")

fit3 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `HIV Prevalence` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = oPaR_binomial, family = binomial(link = "logit"), method = "brglmFit")

tbl1 <- tbl_regression(fit1, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 2)),
               add_estimate_to_reference_rows = TRUE) |> 
     modify_table_body(
       ~mutate(.x, ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

tbl2 <- tbl_regression(fit2, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 2)),
               add_estimate_to_reference_rows = TRUE) |> 
     modify_table_body(
       ~mutate(.x, ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

tbl3 <- tbl_regression(fit3, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 2)),
               add_estimate_to_reference_rows = TRUE) |> 
     modify_table_body(
       ~mutate(.x, ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

# Merge the tables with tab spanners
tbl_merge(
  tbls = list(tbl1, tbl2, tbl3),
  tab_spanner = c("People living with HIV", "Household contacts", "Other people at risk")) |> 
  as_gt() |> 
  gt::gtsave(filename = "../results/tbl3_binomial_multi.docx")
```

# Results for Manuscript

## Summary

-   Of 172 HIV clinics surveyed, 142 (82%) were in Africa, 22 (13%) in the Asia-Pacific and 8 (5%) in Latin America; 108 (63%) were located in urban areas.

    -   See Table 1

-   Twenty-nine (17%) clinics reported using tuberculin skin testing and/or the interferon-gamma release assays to determine TPT eligibility.

    -   See Table 2 (TB infection testing to check eligibility of PLHIV to receive TPT) —\> any of the first 3 resonses (3 + 14 + 12)

-    After ruling out active TB, TPT was reportedly offered to people living with HIV (PLWH) (102 clinics, 60%), household contacts of individuals with active TB (120 clinics, 70%), and other high-risk populations such as health care workers (48 clinics, 28%).

    ```{r}
    prop1 <- df1 |>
      group_by(who_group, variable) |>
      dplyr::summarize(sum = sum(category == "Yes"),
        prop = round(sum(category == "Yes") / n(),2),.groups = "drop") 

    prop2 <- prop1 |>
      group_by(who_group) |>
      dplyr::summarize(mean_n = mean(sum),
        mean_prop = mean(prop)) |>
      ungroup()
    ```

-   Clinics reported use of isoniazid-based (160 clinics, 93%), and shorter rifamycin-based (129 clinics, 75%) TPT regimens. Reported barriers to TPT initiation included patient refusal at 71 (41%) and drug shortages at 67 (39%) clinics.

    ```{r}
    tabyl(df5_model$INH)
    tabyl(df5_model$RIF)

    df2 |> 
      filter(variable == "Patients refuse TPT") |>
      tabyl(category)

    df2 |> 
      filter(variable == "Medication availability") |>
      tabyl(category)
    ```

-   Of the remaining 172 clinics providing TPT, 16 (9%) were in West Africa, 24 (14%) in Central Africa, 71 (41%) in East Africa, 31 (18%) in Southern Africa, 22 (27%) in Asia-Pacific, and 8 (5%) in Latin America and the Caribbean. Most clinics were in urban settings (108, 63%) and fully integrated TB care as part of HIV services was available at 107 clinics (62%) ([Table 1]{.underline}).

    -   See Table 1 and here:

```{r}
df |> 
  group_by(region_exact) |> 
  summarise(n = n(), prop = round(n / nrow(df),2))
```

-   In providing TPT, almost all clinics (171/172) reported using symptom screening for identifying patients with active TB. TB infection testing for TPT eligibility determination among PLWH was done in 29 (23%) clinics, ranging from 12% in Africa, 36% in Asia-Pacific, to 50% in Latin America. Among clinics with TB infection testing, 14/29 (48%) used tuberculin skin testing, 3 (10%) interferon-gamma release assays, and 12 (41%) both ([Table 2]{.underline}).

    ```{r}
    round(14/29,2)
    round(3/29,2)
    round(12/29,2)

    17/142 #12%
    8/22 #36%
    4/8 #50%
    ```

-   Most HIV care clinics reported providing TPT to PLHIV (mean across subgroups: 102, 60%), and to household contacts of people with active TB (mean across subgroups: 120, 70%). TPT was less often provided to other populations at risk (mean across subgroups: 48, 27%) who were also eligible for TPT regardless of their HIV status, including health care workers at 90 (51%), prisoners at 81 (46%) and immigrants from high TB burden countries at 62 (35%) clinics ([Figure 1]{.underline}, [Figure 2]{.underline}).

    ```{r}
    prop1 <- df1 |>
      group_by(who_group, variable) |>
      dplyr::summarize(sum = sum(category == "Yes"),
        prop = round(sum(category == "Yes") / n(),2),.groups = "drop") 

    prop2 <- prop1 |>
      group_by(who_group) |>
      dplyr::summarize(mean_n = mean(sum),
        mean_prop = mean(prop)) |>
      ungroup()
    ```

-   The 6-month isoniazid monotherapy TPT regimen was the most widely offered (155, 90%), followed by the 3-month once-weekly isoniazid-rifapentine regimen (110, 64%). Other short rifamycin-based regimens such as 3-month rifampicin monotherapy were available at 11 (6%) clinics ([Figure 3]{.underline}).

    ```{r}
    df5 |> dplyr::select(record_id, `6-month isoniazid (6H)`, `Once-weekly isoniazid-rifapentine for 12 weeks (3HP)`, `3-month rifampicin (3R)`) |>
      mutate(`6-month isoniazid (6H)` = ifelse(`6-month isoniazid (6H)` %in% c("Adults", "Adults & Children", "Children"),1,0),
             `Once-weekly isoniazid-rifapentine for 12 weeks (3HP)` = ifelse(`Once-weekly isoniazid-rifapentine for 12 weeks (3HP)` %in% c("Adults", "Adults & Children", "Children"), 1, 0),
             `3-month rifampicin (3R)`= ifelse(`3-month rifampicin (3R)` %in% c("Adults", "Adults & Children", "Children"),1,0)) |>
      summarise(sum_6H = sum(`6-month isoniazid (6H)`),
                prop_6H = round(sum_6H / nrow(df5),2),
                sum_3HP = sum(`Once-weekly isoniazid-rifapentine for 12 weeks (3HP)`),
                prop_3HP = round(sum_3HP / nrow(df5),2),
                sum_3R = sum(`3-month rifampicin (3R)`),
                prop_3R = round(sum_3R / nrow(df5),2),)
    ```

-   Once-weekly isoniazid-rifapentine and 3-month isoniazid-rifampicine were more commonly offered in high TB burden countries

    ```{r}
    df5_model |> group_by(HBC_ANY) |> 
      summarize(
        total = n(),
        count = sum(`Once-weekly isoniazid-rifapentine for 12 weeks (3HP)` %in% c("Adults", "Adults & Children", "Children")),
        proportion = round(count / total, 2)) |>gtsummary::tbl_uvregression(
          method = glm,
          include = c(HBC_ANY),
          y = cbind(count, total - count),
          method.args = list(family = binomial(link = "logit")),
          exponentiate = TRUE,
          pvalue_fun = ~style_pvalue(.x, digits = 2))
    ```
