---
title: "Results"
author: "Remo Schmutz"
date: "2024-05-01"
output:
  html_document: 
    fig_caption: true
    code_folding: hide
    highlight: tango
    theme: simplex
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(wesanderson)
library(rnaturalearth)
library(sf)
library(readxl)
library(janitor)
library(paletteer)
library(maps)
library(table1)
library(ggpubr)
library(kableExtra)
library(scales)
library(showtext)
library(jtools)
library(lme4)
library(brglm2)
library(gtsummary)
library(gt)
library(scico)
library(cowplot)
library(MASS)
library(tidyverse)
library(patchwork)

source("../utils/plots.R")

df_both <- readRDS("../data_clean/data_clean.rds")
                          
df <- df_both |>
  filter(tpt_prov == 1)

df_no_TPT <- df_both |>
  filter(tpt_prov == 0)

df1 <- readRDS("../data_clean/df1.rds")
df1_noTPT <- readRDS("../data_clean/df1_withexcluded.rds")
df2 <- readRDS("../data_clean/df2.rds")
df3 <- readRDS("../data_clean/df3.rds")
df4 <- readRDS("../data_clean/df4.rds")
df5 <- readRDS("../data_clean/df5.rds")
df6 <- readRDS("../data_clean/df6.rds")
```

-   The complete dataset includes 235 observations

    -   excluding region North America there are 201 observations left

    -   excluding incomplete responses there are 199 observations left

    -   excluding high income countries there are 178 observations left

    -   excluding sites that do not offer TPT there are 172 observations left

# Data overview

```{r}
#regions
janitor::tabyl(df$region_exact) |>adorn_totals("row") |>
  adorn_pct_formatting(digits = 0)

df |>
  dplyr::select(country, Prev_cat.factor, Income_group) |>
  group_by(country) |>
  summarise(
    `Number of sites` = n(),
    `HIV Prevalence` = first(Prev_cat.factor),  # Assumes all entries are the same per country
    `Income Group` = first(Income_group)  # Assumes all entries are the same per country
  ) |>
  ungroup() |>
  kable() |>
  kable_styling(full_width = T)
```

# Table S1

We excluded six sites from our analysis because they do not offer TPT at the time of the survey.

```{r}
country_lookup <- tibble::tribble(
  ~country_code, ~country_name,
  "IND", "India",
  "ZAF", "South Africa",
  "UGA", "Uganda",
  "KEN", "Kenya",
  "TGO", "Togo"
) 

df_no_TPT <- df_no_TPT |>
  left_join(country_lookup, by = c("country" = "country_code")) |>
  dplyr::select(country_name, name, region, Prev_cat.factor, Income_group, level.factor, tbhiv_integration.factor) |>
  rename(Country = country_name,
         Name = name, 
         Region = region,
         `HIV Prevalence` = Prev_cat.factor,
         `Income Level` = Income_group,
         `Facility level of care` = level.factor,
         `Level of Integration` = tbhiv_integration.factor) |>
  arrange(Country)

df_no_TPT |>
  gt() |>
  cols_label(
    Country = "Country",
    Name = "Name",
    Region = "Region",
    `HIV Prevalence` = "HIV Prevalence",
    `Income Level` = "Income Level",
    `Facility level of care` = "Facility level of care",
    `Level of Integration` = "Level of Integration") |> 
  tab_options(
    table.width = pct(100)) |>
  gt::gtsave(filename = "../results_revision/supplements/tblS1.docx")
```

# Figure 1

This maps the answers from Figure 2 on country level - the answer "Yes" is defined as the answer "Yes" to any of the subquestions within the respective categories (see Figure 2). 

```{r}
coords <- read.csv("../data_clean/coordinates_sites.csv") |> 
  separate(coord, into = c("lat", "long"), sep = ",", convert = TRUE) |>
  filter(record_id %in% df$record_id)

world <- map_data("world") 

df1_map <- df1 |>
  group_by(record_id, who_group) |>
  dplyr::summarize(any_yes = ifelse(any(category == "Yes"), 1, 0), .groups = 'drop')|> # Yes defined as any Yes
  left_join(df |> dplyr::select(record_id, region_exact), by = "record_id") 
 
fig1a <- fig1(variable = "People living with HIV") +
  labs(title = "a | People living with HIV") +
  theme(plot.margin = unit(c(0.5,0,0,0.01), "cm"))

fig1b <- fig1(variable = "Household contacts")  +
  labs(title = "b | Household contacts") +
   theme(plot.margin = unit(c(0,0.01,0,0), "cm"))

fig1c <- fig1(variable = "Other people at risk") +
  labs(title = "c | Other people at risk") +
    theme(plot.margin = unit(c(0,0.01,0,0), "cm")) 

fig.1 <- (fig1a + fig1b + fig1c) +
  plot_layout(ncol = 1, guides = "collect") 
ggsave("../results_revision/main/fig1.tiff", plot = fig.1, width = 12, height = 16, units = "cm", dpi = 300)
```

# Figure 2

Identifying populations for latent TB infection (LTBI) testing and TB preventive treatment after exclusion of active TB. Mapping according to WHO guidelines (see WHO consolidated guidelines, Table 1, page xi). Household contacts are defined as household contacts of people with bacteriologically confirmed pulmonary TB, regardless of HIV status. These three groups are not exclusive, there can be overlap. PLHIV can also be household contacts.

```{r}
fig.2 <- fig2(df1, "", pct = T)
fig.2
ggsave("../results_revision/main/fig2.tiff", plot = fig.2, width = 18, height = 12, units = "cm", dpi = 300)
```

# Figure S1

```{r, fig.height=15, fig.width=11, message=F, warning=F}
figS1a <- fig2(df1, "region") +
  labs(title = "a | By region")

ggsave("../results_revision/supplements/figS1a.png", plot = figS1a, width = 18, height = 12, units = "cm", dpi = 300)

figS1b <- fig2(df1, "HBC_ANY") + 
  labs(title = "b | By TB burden")

ggsave("../results_revision/supplements/figS1b.png", plot = figS1b, width = 18, height = 12, units = "cm", dpi = 300)

figS1c <- fig2(df1, "HIV Prevalence") + 
  labs(title = "c | By national HIV prevalence")

ggsave("../results_revision/supplements/figS1c.png", plot = figS1c, width = 18, height = 12, units = "cm", dpi = 300)

figS1d <- fig2(df1, "Level of integration") + 
  labs(title = "d | By level of HIV/TB service integration")
  
ggsave("../results_revision/supplements/figS1d.png", plot = figS1d, width = 18, height = 12, units = "cm", dpi = 300)
```

# Figure 3

Barriers to TPT administration: \*\*11.15 What are the most important barriers to initiating patients with HIV on TPT at this facility? Check all that apply\*\*  

```{r, fig.cap="Figure 2: Proportion of clinics responding to the questions regarding specific boundaries to initiating patients with HIV on TPT at the clinic. Also, if somebody in the clinic received formal training for TPT."}
fig.3 <- fig3("", pct = T)
fig.3
ggsave("../results_revision/main/fig3.tiff", plot = fig.3, width = 18, height = 12, units = "cm", dpi = 300)
```

# Figure 4

```{r}
fig.4 <- fig4("")
fig.4
ggsave("../results_revision/main/fig4.tiff", plot = fig.4, width = 18, height = 12, units = "cm", dpi = 300)
```

# Figure S2 

```{r, fig.height=15, fig.width=11, message=F, warning=F}
figS2a <- fig4("region") + 
  theme(strip.text.y.right = element_blank(), 
        axis.title.x.bottom = element_blank()) +
  scale_x_continuous(
    labels = function(x) paste0(format(x * 100, digits = 2), "%"),
    breaks = c(0, 1)) +
labs(title = "a | By region")

ggsave("../results_revision/supplements/figS2a.png", plot = figS2a, width = 18, height = 12, units = "cm", dpi = 300)

figS2b <- fig4("HBC_ANY") + 
  theme(axis.text.y.right = element_blank(), 
        axis.title.x.bottom = element_blank()) +  
  scale_x_continuous(
    labels = function(x) paste0(format(x * 100, digits = 2), "%"),
    breaks = c(0, 1))+
  labs(title = "b | By TB burden")

ggsave("../results_revision/supplements/figS2b.png", plot = figS2b, width = 18, height = 12, units = "cm", dpi = 300)

figS2c <- fig4("HIV Prevalence") + 
  theme(axis.text.y.right = element_blank(),
        axis.title.x.bottom = element_blank()) +  
  scale_x_continuous(
      labels = function(x) paste0(format(x * 100, digits = 2), "%"),
      breaks = c(0, 1))+
  labs(title = "c | By national HIV prevalence")

ggsave("../results_revision/supplements/figS2c.png", plot = figS2c, width = 18, height = 12, units = "cm", dpi = 300)

figS2d <- fig4("Level of integration") + 
  theme(axis.text.y.right = element_blank(),
        axis.title.x.bottom = element_blank()) +  scale_x_continuous(
          labels = function(x) paste0(format(x * 100, digits = 2), "%"),
          breaks = c(0, 1))+
  labs(title = "d | By level of HIV/TB service integration")

ggsave("../results_revision/supplements/figS2d.png", plot = figS2d, width = 18, height = 12, units = "cm", dpi = 300)
```

# Table S2

```{r}
tblS2_overall <- df5 |>
  tbl_summary(
              include = c(
                          `Population the center serves`, 
                          `Facility location`, 
                          `Facility level of care`, 
                          `Level of integrated TB/HIV services`),
              digits = list(everything() ~ c(0))) |> 
  modify_header(all_stat_cols(FALSE) ~ "N = {n}") 

tblS2_strata <- df5 |>
  tbl_summary(by = region,
              include = c(
                          `Population the center serves`, 
                          `Facility location`, 
                          `Facility level of care`, 
                          `Level of integrated TB/HIV services`), 
              digits = list(everything() ~ c(0))) |>
   modify_header(all_stat_cols(FALSE) ~ "**{level}**<br>N = {n}")

tbl_merge(
  tbls = list(tblS2_overall, tblS2_strata),
  tab_spanner = c("Overall", "Region")) |> 
  as_gt() |> 
  gt::gtsave(filename = "../results_revision/supplements/tblS2.docx")
```

# Table S3

```{r}
tblS3_overall <- df6 |>
  tbl_summary(
              include = c(`TB symptom screening`, 
                          `Anyone attended a formal training on TPT provision`,
                          `TB infection testing to check eligibility of PLHIV to receive TPT`),
              digits = list(everything() ~ c(0))) |>
  modify_header(stat_0 ~ "N = {n}")

tblS3_strata <- df6 |>
  tbl_summary(by = region,
              include = c(`TB symptom screening`, 
                          `Anyone attended a formal training on TPT provision`,
                          `TB infection testing to check eligibility of PLHIV to receive TPT`),
              digits = list(everything() ~ c(0))) |>
  modify_header(all_stat_cols(FALSE) ~ "**{level}**<br>N = {n}")

tbl_merge(
  tbls = list(tblS3_overall, tblS3_strata),
  tab_spanner = c("Overall", "Region")) |> 
  as_gt() |> 
  gt::gtsave(filename = "../results_revision/supplements/tblS3.docx")
```

# Table S4

Associations with RIF-based regimen

## Univariable / Multivariable

```{r, warning=FALSE}
# the warning message Warning :non-integer #successes in a binomial glm! comes from the weights brglmFit uses and can be ignored accoring to the documentary https://rdrr.io/cran/WeightIt/src/R/weightit2glm.R
df3_model <- df3 |>
  mutate(
         RIF = as.integer(if_any(c("3-month rifampicin (3R)",
                                                        "4-month rifampicin (4R)",
                                                        "3-month isoniazid-rifampicin (3HR)",
                                                        "4-month isoniazid-rifampicin (4HR)",
                                                        "Once-weekly isoniazid-rifapentine for 12 weeks (3HP)",
                                                        "Once-daily isoniazid-rifapentine for 1 month (1HP)"), ~ .x %in% c("Adults only", "Children only", "Adults & Children"))),
         INH = as.integer(if_any(c("6-month isoniazid (6H)",
                                                        "9-month isoniazid (9H)",
                                                        "12-month isoniazid (12H)",
                                                        "36/Lifetime isoniazid (36/Lifetime H)"), ~ .x %in% c("Adults only", "Children only", "Adults & Children"))),
         RIF = factor(RIF, levels = c(0, 1)))

df3_model$`Income Level` <- droplevels(df3_model$`Income Level`)
df3_model$HBC_ANY <- relevel(df3_model$HBC_ANY, ref = "No")
df3_model$region <- relevel(df3_model$region, ref = "Asia-Pacific")
df3_model$`Level of integration` <- relevel(df3_model$`Level of integration`, ref = "Full")
df3_model$`HIV Prevalence` <- relevel(df3_model$`HIV Prevalence`, ref = "High")
df3_model$`Income Level` <- relevel(df3_model$`Income Level`, ref = "Upper middle")

# univariable

tbls4_uni2 <- df3_model |>
    tbl_uvregression(include = c(`Level of integration`,
                                 `Income Level`,
                                 `HIV Prevalence`,
                                 HBC_ANY,
                                 `TPT training`,
                                 `Facility level of care`,
                                 region),
      method = glm,
      y = RIF,
      method.args = list(family = binomial(link = "logit"), method = "brglmFit"), 
      pvalue_fun = ~ifelse(. < 0.01, "<0.01", style_sigfig(., digits = 2)),
      exponentiate = TRUE,
      hide_n = TRUE, add_estimate_to_reference_rows = TRUE, 
      label = list(region ~ "Region",
                   HBC_ANY ~ "High burden country")) |> 
  modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |> 
  add_global_p()

# multivariable 
#' I also exclude the variable HIV prevalence as in Table 1

fit1 <- glm(RIF ~ `Level of integration`+ 
                                 `Income Level` +
                                 HBC_ANY +
                                 `TPT training` +
                                 `Facility level of care` +
                                 region, 
           data = df3_model, 
           family = binomial(link = "logit"), method = "brglmFit")

tbls4_multi <- tbl_regression(fit1, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 3)),
               add_estimate_to_reference_rows = TRUE,
               label = list(region ~ "Region",
                   HBC_ANY ~ "High burden country")) |>  
      modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

# merge

tbl_merge(tbls = list(tbls4_uni, tbls4_multi), tab_spanner = c("Univariable", "Multivariable")) |> 
  as_gt() |> 
  gt::gtsave(filename = "../results_revision/supplements/tblS4.docx")
```

# Table 1

We examined the association between clinic and country-level characteristics and the degree of adherence to WHO recommendations across three populations eligible for TPT: people living with HIV (PLHIV), household contacts of people with TB, and other populations at risk.

Rather than using a binary outcome (e.g., adherence to any recommendation), we modeled the number of recommendations adhered to versus the number not adhered to as a binomial outcome for each clinic. This approach allows us to capture the gradient of adherence rather than a simple yes/no indicator.

For each subgroup, we conducted univariable Firth-corrected logistic regression models to estimate the association between each covariate and adherence to recommendations. Firth logistic regression was used to address issues of complete separation in the data.

## Univariable

```{r, warning = FALSE}
df7_binomial <- df1 |>
  mutate(Yes = ifelse(category == "Yes", 1, 0),
         No = ifelse(category == "No", 1, 0)) |>
  group_by(record_id, who_group) |>
  dplyr::summarize(yes = sum(Yes),
                   no = sum(No), .groups = "drop") |>
  left_join(df |> 
              dplyr::select(record_id, tbhiv_integration.factor, Income_group, Prev_cat.factor, HBC_ANY,
                            tpt_training.factor, level.factor, region), by = "record_id") |>
  rename(
    'Level of integration' = tbhiv_integration.factor,
    'Income Level' = Income_group, 
    'HIV Prevalence' = Prev_cat.factor,
    'High burden country' = HBC_ANY,
    'TPT training' = tpt_training.factor,
    'Facility level of care' = level.factor,
    'Region' = region) |>
  mutate(`Income Level` = as.factor(`Income Level`),
         `TPT training` = as.factor(case_when(`TPT training` %in% c(NA, "Dont Know") ~ NA,
                                    TRUE ~ `TPT training`))) |> 
  ungroup()

df7_binomial$`Level of integration` <- relevel(df7_binomial$`Level of integration`, ref = "No")
df7_binomial$`Income Level` <- relevel(df7_binomial$`Income Level`, ref = "Upper middle")
df7_binomial$`HIV Prevalence` <- relevel(df7_binomial$`HIV Prevalence`, ref = "Low")
df7_binomial$`TPT training` <- relevel(df7_binomial$`TPT training`, ref = "No")
df7_binomial$`TPT training` <- droplevels(df7_binomial$`TPT training`)
df7_binomial$`Facility level of care` <- relevel(df7_binomial$`Facility level of care`, ref = "District hospital")
df7_binomial$`Facility level of care` <- droplevels(df7_binomial$`Facility level of care`)
df7_binomial$Region <- relevel(df7_binomial$Region, ref = "Africa")
df7_binomial$`High burden country` <- relevel(df7_binomial$`High burden country`, ref = "No")
df7_binomial$`Income Level` <- droplevels(df7_binomial$`Income Level`)

plhiv_binomial <- df7_binomial |> 
  filter(who_group == "People living with HIV") |>
  dplyr::select(-record_id, -who_group)

household_binomial <- df7_binomial |>
  filter(who_group == "Household contacts") |>
  dplyr::select(-record_id,-who_group)

oPaR_binomial <- df7_binomial |>
  filter(who_group == "Other people at risk") |>
  dplyr::select(-record_id, -who_group) 

fit_model_uni_binomial <- function(data) {
  data |>
    tbl_uvregression(
      y = cbind(yes, no),
    formula = "{y} ~ {x}",
    exponentiate = TRUE,
    method = glm,
    method.args = list(family = binomial(link= "logit"), method = "brglmFit"),
       pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 3)),
       hide_n = TRUE, 
       add_estimate_to_reference_rows = TRUE) |> 
      modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()
}

# Combine datasets into a list
dataset_list_binomial <- list(plhiv_binomial,household_binomial,oPaR_binomial)

# Apply the univariate model function to each dataset
tbls_binom <- lapply(dataset_list_binomial, fit_model_uni_binomial)

# Merge the tables with tab spanners
tbl_merge(
  tbls = tbls_binom,
  tab_spanner = c("People living with HIV", "Household contacts", "Other people at risk")) |> 
  as_gt() |> 
  gt::gtsave(filename = "../results_revision/main/tbl1_univariable.docx")
```

## Multivariable

### Complete

Including all variables that are used in the univariable analysis.

```{r, warning = FALSE}
fit1 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `HIV Prevalence` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = plhiv_binomial, family = binomial(link = "logit"), method = "brglmFit")
car::vif(fit1)

fit2 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `HIV Prevalence` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = household_binomial, family = binomial(link = "logit"), method = "brglmFit")

car::vif(fit2)

fit3 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `HIV Prevalence` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = oPaR_binomial, family = binomial(link = "logit"), method = "brglmFit")

car::vif(fit3)

tbl1 <- tbl_regression(fit1, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 3)),
               add_estimate_to_reference_rows = TRUE) |> 
      modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

tbl2 <- tbl_regression(fit2, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 3)),
               add_estimate_to_reference_rows = TRUE) |> 
      modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

tbl3 <- tbl_regression(fit3, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 3)),
               add_estimate_to_reference_rows = TRUE) |> 
     modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

# Merge the tables with tab spanners
tbl_merge(
  tbls = list(tbl1, tbl2, tbl3),
  tab_spanner = c("People living with HIV", "Household contacts", "Other people at risk")) |> 
  as_gt() |> 
  gt::gtsave(filename = "../results_revision/supplements/tbl1_multi.docx")
```

### Subsample of variables

We calculated the VIF for the complete model and excluded the variable `HIV Prevalence` due to a VIF value around 4 for all three outcomes. After excluding this variable, the VIF values for the remaining variables are all around 1.
 
```{r}
fit1 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = plhiv_binomial, family = binomial(link = "logit"), method = "brglmFit")

car::vif(fit1)

fit2 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = household_binomial, family = binomial(link = "logit"), method = "brglmFit")

car::vif(fit2)

fit3 <- glm(cbind(yes, no) ~ `Level of integration` + `Income Level` + `High burden country` + `TPT training` + `Facility level of care` + Region, 
           data = oPaR_binomial, family = binomial(link = "logit"), method = "brglmFit")

car::vif(fit3)

tbl1 <- tbl_regression(fit1, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 3)),
               add_estimate_to_reference_rows = TRUE) |> 
      modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

tbl2 <- tbl_regression(fit2, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 3)),
               add_estimate_to_reference_rows = TRUE) |> 
      modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

tbl3 <- tbl_regression(fit3, 
               exponentiate = TRUE,
               pvalue_fun = ~ifelse(. < 0.001, "<0.001", style_sigfig(., digits = 3)),
               add_estimate_to_reference_rows = TRUE) |> 
      modify_table_body(
      ~mutate(.x,
          estimate = ifelse(reference_row == TRUE, 1, estimate),
          ci = ifelse(reference_row == TRUE, "Reference", ci))) |>
     add_global_p()

# Merge the tables with tab spanners
tbl_merge(
  tbls = list(tbl1, tbl2, tbl3),
  tab_spanner = c("People living with HIV", "Household contacts", "Other people at risk")) |> 
  as_gt() |> 
  gt::gtsave(filename = "../results_revision/supplements/tbl1_multi_subset.docx")
```

## Sensitivity Analysis - Including the previously excluded sites

I re-run everything separately in order to make sure nothing is overwritten. This analysis is done because of a comment of a reviewer but will not be further used. 

```{r, warning = FALSE}
df7sens_binomial <- df1_noTPT |>
  mutate(Yes = ifelse(category == "Yes", 1, 0),
         No = ifelse(category == "No", 1, 0)) |>
  group_by(record_id, who_group) |>
  dplyr::summarize(yes = sum(Yes),
                   no = sum(No), .groups = "drop") |>
  left_join(df_both |> 
              dplyr::select(record_id, tbhiv_integration.factor, Income_group, Prev_cat.factor, HBC_ANY,
                            tpt_training.factor, level.factor, region), by = "record_id") |>
  rename(
    'Level of integration' = tbhiv_integration.factor,
    'Income Level' = Income_group, 
    'HIV Prevalence' = Prev_cat.factor,
    'High burden country' = HBC_ANY,
    'TPT training' = tpt_training.factor,
    'Facility level of care' = level.factor,
    'Region' = region) |>
  mutate(`Income Level` = as.factor(`Income Level`),
         `TPT training` = as.factor(case_when(`TPT training` %in% c(NA, "Dont Know") ~ NA,
                                    TRUE ~ `TPT training`))) |> 
  ungroup()

df7sens_binomial$`Level of integration` <- relevel(df7sens_binomial$`Level of integration`, ref = "No")
df7sens_binomial$`Income Level` <- relevel(df7sens_binomial$`Income Level`, ref = "Upper middle")
df7sens_binomial$`HIV Prevalence` <- relevel(df7sens_binomial$`HIV Prevalence`, ref = "Low")
df7sens_binomial$`TPT training` <- relevel(df7sens_binomial$`TPT training`, ref = "No")
df7sens_binomial$`TPT training` <- droplevels(df7sens_binomial$`TPT training`)
df7sens_binomial$`Facility level of care` <- relevel(df7sens_binomial$`Facility level of care`, ref = "District hospital")
df7sens_binomial$`Facility level of care` <- droplevels(df7sens_binomial$`Facility level of care`)
df7sens_binomial$Region <- relevel(df7sens_binomial$Region, ref = "Africa")
df7sens_binomial$`High burden country` <- relevel(df7sens_binomial$`High burden country`, ref = "No")
df7sens_binomial$`Income Level` <- droplevels(df7sens_binomial$`Income Level`)

plhiv_binomialsens <- df7sens_binomial |> 
  filter(who_group == "People living with HIV") |>
  dplyr::select(-record_id, -who_group)

household_binomialsens <- df7sens_binomial |>
  filter(who_group == "Household contacts") |>
  dplyr::select(-record_id,-who_group)

oPaR_binomialsens <- df7sens_binomial |>
  filter(who_group == "Other people at risk") |>
  dplyr::select(-record_id, -who_group) 

# Combine datasets into a list
dataset_list_binomial_sens <- list(plhiv_binomialsens,household_binomialsens,oPaR_binomialsens)

# Apply the univariate model function to each dataset
tbls_binom_sens <- lapply(dataset_list_binomial_sens, fit_model_uni_binomial)

# Merge the tables with tab spanners
tbl_merge(
  tbls = tbls_binom_sens,
  tab_spanner = c("People living with HIV", "Household contacts", "Other people at risk")) 
  as_gt() |> 
  gt::gtsave(filename = "../results_revision/supplements/tbl1_univariable_including6clinics.docx")
```

# Results for Manuscript text

## Summary

### Results

Most of the relevant numbers can be directly read out from the tables. There are some percentages which have to be manually calculated. Numbers that can be directly read out from the tables are directly inserted, all others are calculated below:

`Of xxx HIV clinics surveyed, xxx (xxx%) were in Africa, xxx (xxx%) in the Asia-Pacific and 8 (xxx%) in Latin America; xxx (xxx%) were located in urban areas.`

The raw numbers can be read out from Table S2. The percentages are calculated below:

```{r}
round(142/172,2)
round(22/172,2)
round(8/172,2)
```

`xxx (xxx%) clinics reported using tuberculin skin testing and/or interferon-gamma release assays to determine TPT eligibility.`

This can be read out from table S3 by adding Interferon-Gamma Release Assays blood test + Tuberculin Skin Test + both (3 + 14 + 12 = 29) and their respective percentages (2 + 8 + 7 = 17%).

After ruling out active TB, TPT was reportedly offered to PLWH (xxx clinics, xxx%), household contacts of individuals with active TB (xxx clinics, xxx%), and other high-risk populations, including healthcare workers (xxx clinics, xxx%).

Should we use any yes as the outcome variable? 

```{r}
prop1 <- df1 |>
      group_by(who_group, variable) |>
      dplyr::summarize(sum = sum(category == "Yes"),
        prop = round(sum(category == "Yes") / n(),2),.groups = "drop") 
prop2 <- prop1 |>
      group_by(who_group) |>
      dplyr::summarize(mean_n = mean(sum),
        mean_prop = mean(prop)) |>
      ungroup()
```


`Clinics reported use of isoniazid-based (xxx clinics, xxx%) and shorter rifamycin-based (xxx clinics, xxx%) TPT regimens.`

```{r}
summ <- df3 |> 
  mutate(
         RIF = as.integer(if_any(c("3-month rifampicin (3R)",
                                                        "4-month rifampicin (4R)",
                                                        "3-month isoniazid-rifampicin (3HR)",
                                                        "4-month isoniazid-rifampicin (4HR)",
                                                        "Once-weekly isoniazid-rifapentine for 12 weeks (3HP)",
                                                        "Once-daily isoniazid-rifapentine for 1 month (1HP)"), ~ .x %in% c("Adults only", "Children only", "Adults & Children"))),
         INH = as.integer(if_any(c("6-month isoniazid (6H)",
                                                        "9-month isoniazid (9H)",
                                                        "12-month isoniazid (12H)",
                                                        "36/Lifetime isoniazid (36/Lifetime H)"), ~ .x %in% c("Adults only", "Children only", "Adults & Children"))))

summ |> 
  tabyl(RIF) |> 
  mutate(percent = round(percent, 2))

summ |>
  tabyl(INH) |> 
  mutate(percent = round(percent, 2))
```

`Reported barriers to TPT initiation included patient refusal at xxx (xxx%) and drug shortages at xxx (xxx%) clinics.`

```{r}
df2 |> 
  filter(variable == "Patients refuse TPT") |>
  tabyl(category) |> 
  mutate(percent = round(percent, 2))

df2 |> 
  filter(variable == "Medication availability") |>
  tabyl(category) |> 
  mutate(percent = round(percent, 2))
```

## Results

### Participating HIV care clinics

`The survey was distributed to 180 HIV care clinics in LMICs, and 178 completed the questionnaire (xxx%); 6 (xxx%) facilities reported that TPT was not available at their site and were therefore excluded from subsequent analysis (Supplementary Table S1).`

This is not directly reported anywhere.

```{r}
round(178/180,2)
round(6/178,2)
```

`Of the remaining 172 clinics providing TPT, 16 (9%) were in West Africa, 24 (14%) in Central Africa, 71 (41%) in East Africa, 31 (18%) in Southern Africa, 22 (13%) in the Asia-Pacific, and 8 (5%) in Latin America and the Caribbean.`

```{r}
df |> 
  tabyl(region_exact) |> 
  mutate(percent = round(percent, 2))
```
`Most clinics were in urban settings (108, 63%), and fully integrated TB care as part of HIV services was available at 107 clinics (62%) (Supplementary Table S2). The provision of any TPT training to healthcare workers varied from 50% to 100% depending on the region (Supplementary Table S3).`

This can all be directly read out from Table S2 and S3

### Implementation of TPT according to WHO recommendations

#### TB screening and testing

`In providing TPT, almost all clinics (171/172) reported using symptom screening for identifying patients with active TB.`

This can be read out from table S3. Only 1 clinic did not respond Yes to the TB symptom sceening question. 

`TB infection testing for TPT eligibility determination among PLWH was done in xxx (xxx%) clinics, ranging from xxx% in Africa, xxx% in the Asia-Pacific, to xxx% in Latin America.`

These values can be mostly read out from Table S3 but some calculations are necessary. Adding Interferon-Gamma Release Assays blood test + Tuberculin Skin Test + both (3 + 14 + 12 = 29) and their respective percentages (2 + 8 + 7 = 17%). The country-wise percentages need to be manually calculated

```{r}
round((1 + 13 + 3) / 142, 2) # Africa
round((2 + 1 + 5) / 22, 2) # Asia-Pacific
round((0 + 0 + 4) / 8, 2) # Latin America
```

`Among clinics with TB infection testing, xxx/xxx (xxx%) used tuberculin skin testing, xxx (xxx%) interferon-gamma release assays, and xxx (xxx%) used both (Supplementary Table S3).`

```{r}
round(14 / (14 + 3 + 12), 2) # TST
round(3 / (14 + 3 + 12), 2) # IGRA
round(12 / (14 + 3 + 12), 2) # both
```

#### Eligible populations, associated factors, and barriers 

`Most HIV care clinics reported providing TPT to PLHIV (mean across subgroups: xxx, xxx%; range: [xxx,xxx]), and to household contacts of people with active TB (mean across subgroups: 120, 70%; range: [xxx,xxx]). TPT was less often provided to other populations at risk (mean across subgroups: 48, 27%; range: [xxx,xxx]) who were also eligible for TPT regardless of their HIV status, including health care workers at xxx (xxx%), prisoners at xxx (xxx%) and immigrants from high TB burden countries at xxx (xxx%) clinics ([Figure 1], [Figure 2]).`

```{r}
prop_subgroup <- df1 |>
  group_by(who_group, variable) |>
  dplyr::summarize(sum = sum(category == "Yes"),
                   prop = round(sum(category == "Yes") / n(),2),.groups = "drop") 

prop_group <- prop_subgroup |>
  group_by(who_group) |>
  dplyr::summarize(mean_n = mean(sum),
                   min_prop = min(prop),
                   max_prop = max(prop),
                   mean_prop = mean(prop)) |>
  ungroup()
```

`The most frequently reported barriers to TPT uptake were patient refusal (71, 41%), followed by insufficient drug availability or shortages (67, 39%).  (Figure 3).`

```{r}
df2 |> 
  filter(variable %in% c("Patients refuse TPT", "Medication availability", "No barriers")) |> 
  group_by(variable) |>
  summarise(n = n(),
            yes = sum(category == "Yes"),
            percent = yes/n)
```

#### Available TPT regimens and associated factors

`The 6-month isoniazid monotherapy TPT regimen was the most widely offered (155, 90%), followed by the 3-month once-weekly isoniazid-rifapentine regimen (110, 64%). Other short rifamycin-based regimens such as 3-month rifampicin monotherapy were available at 11 (6%) clinics (Figure 4). The availability of TPT regimens stratified by region, TB burden, national HIV prevalence, and by the level of HIV/TB service integration is shown in Supplementary Figure S2. The use of any short-course rifamycin-based regimen was not clearly associated with clinic characteristics, including region, TB burden, HIV prevalence, or country income level.`

```{r}
df3 |> dplyr::select(record_id, `6-month isoniazid (6H)`, `Once-weekly isoniazid-rifapentine for 12 weeks (3HP)`, `3-month rifampicin (3R)`) |>
      mutate(`6-month isoniazid (6H)` = ifelse(`6-month isoniazid (6H)` %in% c("Adults only", "Adults & Children", "Children only"),1,0),
             `Once-weekly isoniazid-rifapentine for 12 weeks (3HP)` = ifelse(`Once-weekly isoniazid-rifapentine for 12 weeks (3HP)` %in% c("Adults only", "Adults & Children", "Children only"), 1, 0),
             `3-month rifampicin (3R)`= ifelse(`3-month rifampicin (3R)` %in% c("Adults only", "Adults & Children", "Children only"),1,0)) |>
      summarise(sum_6H = sum(`6-month isoniazid (6H)`),
                prop_6H = round(sum_6H / nrow(df3),2),
                sum_3HP = sum(`Once-weekly isoniazid-rifapentine for 12 weeks (3HP)`),
                prop_3HP = round(sum_3HP / nrow(df3),2),
                sum_3R = sum(`3-month rifampicin (3R)`),
                prop_3R = round(sum_3R / nrow(df3),2),)
```
`The majority (xx%) of clinics in our study offered shorter rifamycin-based TPT regimens, albeit mainly for adults.`

```{r}
tabyl(df3_model$RIF)
tabyl(df3_model$INH)
```

`Provision of 3HP a short rifamycin-based regimen (3 months isoniazid/rifapentine) has increased more than six-fold to 64% in this study, reflecting global efforts to expand access to short-course TPT regimens.`

```{r}
tabyl(df3$`Once-weekly isoniazid-rifapentine for 12 weeks (3HP)`)
```


